Fast Sorting on Modern Computers

### 2005-08-02 docs/tech_report/heap.tex
minor changes mergeed in david's heap changes

\section{Predictor Results}

@@

>>>>

\section{A more detailed look at branch prediction}

@@

In order to explore the behaviour of the individual branches in
heapsort, we performed a second set of branch prediction
experiments. Rather than using SimpleScalar, we instead added
additional statements to the heapsort source code to simulate a
separate bimodal predictor for each branch. This allowed us to measure
each branch individually, whereas SimpleScalar gives only a total
figure for all branches. An additional advantage is that the resulting
compiled simulation is much faster than a full microarchitecture
simulator, and we were thus able to take the average of thousands of
runs (\textbf{TODO find out exact number}), rather than the small
number of runs possible with SimpleScalar. For these experiments,
randomly generated array of size \textbf{xxxxx} were used.

\textbf{[David] I am confused by this chart, because the labelling is
a bit unclear. There appears to be a base heapsort, a 4-way cache
heapsort and an 8-way cache heapsort. But the labelling doesn't tell
us this.}

Figure \ref{base and cache heapsorts-1}(a) shows the behaviour of each
branch in the base heapsort algorithm. The ``creation, has children'' branch
is from line \textbf{xxxxx} of Figure \ref{Simple Base Heapsort}.

\textbf{[David] We need to find some way to describe what each of these
branches is. I don't know myself, so the general reader really, really
won't know.}
